Spin canonical divisors of log stacky curves

### 2015-06-27 stacky_write_up/spin_cring.tex

\begin{lem}
\label{lem:sat-3}
\todo{Make explicit assumptions on genus.}
Suppose $L'$ is a log half-canonical divisor of $\sx$ with course
space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ with $R_
{\halfcan'} = k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Let $L = L' + \frac
{1}{3}P$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}

@@

Let $I$ be the ideal generated by these relations in
$k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}]$. Under grlex with
$x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$), the initial ideal of $I$ is \todo{This will only be the case if $a_1,b_1 \neq 0$. We can definitely make this hold if we set up the variables in the right way, but I'm not sure if it's always true.}
\[
	in_\prec(I) = \langle x_{5, 1}^2, x_{7, 1}^2 \rangle
\]

>>>>

\begin{lem}
\label{lem:sat-3}
\todo{Make explicit assumptions on genus.}
Suppose $L'$ is a log half-canonical divisor of $\sx'$ with course
space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ with $R_
{\halfcan'} = k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Let $L = L' + \frac
{1}{3}P$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}

@@

Let $I$ be the ideal generated by these relations in
$k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}]$. Under grlex with
$x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$, the initial ideal of $I$ is \todo{This will only be the case if $a_1,b_1 \neq 0$. We can definitely make this hold if we set up the variables in the right way, but I'm not sure if it's always true.}
\[
	in_\prec(I) = \langle x_{5, 1}^2, x_{7, 1}^2 \rangle
\]
